---
title: "Analyses"
author: "Ari Cross"
date: "2024-11-14"
output: pdf_document
---

# **Marching to Our Own Beat: The Intersection of Identity and Activism**

\
This is a study conducted by a course on political psychology within the Psychology Department at Smith College. The aim of this study is to examine the political attitudes of Smith College students and their involvement or uninvolvement in performative activism. Here, I want to perform some analyses on quantitative data obtained from a self-reported Qualtrics survey

```{r}
#import data
#change to your own file path as needed

library(readr)
data <- read_csv("Data/PSY 375 Data Set - Sheet1 (2).csv")
#View(data)
```

This code chunk is cleaning the 'data' data frame which is the google sheet shared among the researchers within the course.

```{r}
library(tidyverse)
library(tidyr)
#get rid of NAs
data <- data %>% drop_na(`Please enter your researcher-given pseudonym below`)

#omit cyrus
data <- data[-c(13), ]

#take only the first 52 rows
data <- data[1:53, ]
```

In these code chunks I want to import/clean data from the recorded interviews to prepare them for regression analyses.

```{r}
#import csv
library(readr)
df <- read_csv("~/Downloads/Psy 370- For regressions - Sheet1.csv")
#View(df)
```

Cleaning -- converting the color of the county to a numeric value

```{r}
library(tidyverse)
df %>% 
  mutate(county = case_when(`County Color` == 0 ~ "Red",
                             `County Color` == 1 ~ "Blue"))
```

Join data frames based on researcher psuedonym

```{r}
#first replace the blank spaces in df with dashes to match the structure of data 
df$Interviewee <- df$Interviewee %>%
  str_replace_all(" ", "-")

#change both column names to match
df$pseudonym <- df$Interviewee
data$pseudonym <- data$`Please enter your researcher-given pseudonym below`

#more  cleaning for case sensitivity
df$pseudonym <- tolower(df$pseudonym)
data$pseudonym <- tolower(data$pseudonym)

#the data df also has spaces in the pseudonym row
data$pseudonym <- data$pseudonym %>%
  str_replace_all(" ", "-")

#pv is missing a dash in the class df
library(dplyr)
library(stringr)
rows_to_modify <- c(32:37)  #specify the rows you want to change

#modify the specified rows

#add a dash between the 2nd and 3rd characters for the specified row
data$pseudonym[rows_to_modify] <- paste0(
  substr(data$pseudonym[rows_to_modify], 1, 2), "-",
  substr(data$pseudonym[rows_to_modify], 3, nchar(data$pseudonym[rows_to_modify]))
)

#join data frames based on the common key
joined_df <- inner_join(x = df, y = data, by = "pseudonym")
```

This code chunk is the regression displaying the linear relationship between whether the county being red or blue is an indicator of one's knowledge of the term performative activism.

```{r}
library(moderndive)

# Ensure categorical variables are converted to factors
df$county <- as.factor(df$`County Color`)

# Fit the linear regression model
model1 <- lm(`PA-knowledge` ~ county, data = df)


# View the summary of the model
summary(model1)
get_regression_table(model1)
```

This code chunk is the regression which analyzes the relationship between

```{r}
model2<- lm(`How much interest do you generally have in what is going on in politics?` ~
PPA              )
```

Visualizing

```{r}
#first I want to create a bar plot that visualizes the distribution of 
ggplot(df, aes(x=county, y = value)) + 
  geom_bar(stat = "identity")

```

This code chunk will filter the world.cities df for all of the cities located in

In the following code chunks I want to make a map plotting the worldly demographics of each of the participants in my study.

Cleaning

```{r}
#load our packages
library(maps) 
library(plotly)
library(ggiraph)
library(widgetframe)
data(world.cities)

#doing some cleaning of my df
city_list <- joined_df %>%
  #split the "cities" column into separate rows
  separate_rows(`In what city, state, and country did you spend most of your time when you were growing up?`, sep = ", ") %>%
  #extract unique city names
  distinct(`In what city, state, and country did you spend most of your time when you were growing up?`)

#clean the name column -- it contains a ` that won't be compatible with the search column
#filter the world.cities data frame
filtered_cities <- world.cities %>%
  filter(name %in% city_list$`In what city, state, and country did you spend most of your time when you were growing up?`)

#view the result
print(filtered_cities)
#extract the specific row from the larger data frame
row_to_add <- world.cities[16196, ]

#add jerusalem
filtered_cities <- rbind(filtered_cities, row_to_add)
#success
#it looks like it grabbed every double as well so lets filter for what countries actually exist in our df which is ("USA", "Belgium", "Mexico", "Israel")
filtered_cities <- filtered_cities %>% filter(country.etc %in% c("USA", "Belgium", "Mexico", "Israel"))
```

Plotting

```{r}

#create a data frame that is filtered by the city names exiting in the joined df 
caps <- dplyr::filter(world.cities, capital == 1)
caps$population <- prettyNum(caps$pop, big.mark = ",")
plot <- suppressWarnings(figure(width = 800, height = 450, padding_factor = 0) %>%
  ly_map("world", col = "gray") %>%
  ly_points(long, lat, data = caps, size = 5,
            hover = c(name, country.etc, population)))

widgetframe::frameWidget(plot,width=600,height=400)


# Load required libraries
library(ggplot2)
library(maps)

# Get world map data
world <- map_data("world")

# Create the plot
ggplot() +
  geom_polygon(data = world, aes(x = long, y = lat, group = group), fill = "lightgray", color = "white") +
  geom_point(data = filtered_cities, aes(x = long, y = lat), color = "red", size = 2) +
  theme_minimal() +
  labs(title = "PSY 375 Study Participant Hometowns", x = "Longitude", y = "Latitude")

```

```{r}
library(ggplot2)
library(maps)
library(ggthemes) # For additional themes

# World map data
world <- map_data("world")

# Enhanced plot
ggplot() +
  # Draw the world map with subtle styling
  geom_polygon(data = world, aes(x = long, y = lat, group = group), 
               fill = "lightblue", color = "gray70") +
  
  # Add city points
  geom_point(data = filtered_cities, aes(x = long, y = lat), 
             color = "darkred", size = 3, alpha = 0.8, shape = 21, fill = "red") +
  
  # Add city labels
  geom_text(data = filtered_cities, aes(x = long, y = lat, label = name), 
            color = "black", size = 3, nudge_y = 2) +
  
  # Improve theme
  theme_minimal(base_size = 14) +
  theme(
    panel.background = element_rect(fill = "aliceblue", color = NA),
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.margin = margin(10, 10, 10, 10)
  ) +
  
  # Add titles and labels
  labs(
    title = "PSY 375 Study Participant Hometowns",
    subtitle = "",
    x = "Longitude",
    y = "Latitude"
  )

```
